---
output: html_document
---

```{r, include=FALSE}
#source("../../../../../../../../R/Functions.R", local = knitr::knit_global())
```

A table summarising currently available ready4 module libraries can be retrieved from an online repository by using the `get_libraries_tb` function from the ready4 [framework library](docs/getting-started/software/libraries/types/framework/).

```{r include=T}
library(ready4)
```

```{r include=T}
libraries_tb <- get_libraries_tb() %>% update_libraries_tb(include_1L_chr = "modules")#make_libraries_tb("modules")
```

Module libraries are thematically grouped under one of four "sections" of the ready4 model, one each for modelling [People](/docs/model/modules/using-modules/people/), [Places](/docs/model/modules/using-modules/places/), [Platforms](/docs/model/modules/using-modules/platforms/) and [Programs](/docs/model/modules/using-modules/programs/). We can use the `print_packages` function to display the module libraries currently available for each section (currently, there are no publicly available libraries of ready4 modules for modelling platforms).

### Module libraries for modelling people

```{r echo=T}
print_packages(libraries_tb %>% dplyr::filter(Section == "People"))
```

### Module libraries for modelling places

```{r echo=T}
print_packages(libraries_tb %>% dplyr::filter(Section == "Places"))
```

### Module libraries for modelling programs
```{r, include=FALSE}
source("../../../../../../../R/Functions.R", local = knitr::knit_global())
```
```{r echo=T}
print_packages(libraries_tb %>% dplyr::filter(Section == "Programs"))
```
