---
title: "Author Scientific Summaries Of Studies Using The Ready4 Framework"
output: 
  rmarkdown::html_vignette:
    toc: true
  pdf_document:
    highlight: null
    number_sections: yes
vignette: >
  %\VignetteIndexEntry{Author Scientific Summaries Of Studies Using The Ready4 Framework}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---
```{r echo = F}
knitr::opts_chunk$set(echo = TRUE)
```
```{r message=FALSE, warning=FALSE}
library(ready4)
library(ready4show)
library(bookdown)
library(rticles)
```

## Motivation
Open science workflows should ideally span an unbroken chain between data-ingest to production of a scientific summary such as a manuscript. Such extensive workflows provide an explicit means of linking all content in a scientific summary with the analysis that it reports. 

## Implementation
`ready4show` includes a number of classes and methods that help integrate manuscript authoring into a reproducible workflow. These tools are principally intended for use with the [ready4 youth mental health system model](https://www.ready4-dev.com).

### Create a synopsis of the manuscript to be authored
To start with we create `X`, an instance of `Ready4showSynopsis`, a ready4 module (S4 class). We can use `X` to record metadata about the manuscript to be authored (including details about the study being summarised and the title and format of the intended output).

```{r}
X <- Ready4showSynopsis(background_1L_chr = "Our study is entirely fictional.",
                        coi_1L_chr = "None declared.",
                        conclusion_1L_chr = "These fake results are not interesting.",
                        digits_int = 3L,
                        ethics_1L_chr = "The study was reviewed and granted approval by Awesome University's Human Research Ethics Committee (1111111.1).",
                        funding_1L_chr = "The study was funded by Generous Benefactor.",
                        interval_chr = "three months",
                        keywords_chr = c("entirely","fake","do", "not","cite"),
                        outp_formats_chr = "PDF",
                        sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
                        title_1L_chr = "A hypothetical study using fake data")
```

### Add authorship details
Authorship details can be added to slots of `X` that contain `ready4show_authors` and `ready4show_instututes` ready4 sub-modules.

As we can see from the below call to `exhibitSlot`, `X` was created with no authorship information.

```{r}
exhibitSlot(X,
            "authors_r3",
            scroll_box_args_ls = list(width = "100%")) 
```

We can add details on each author by repeated calls to the `renewSlot` method.